Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-07-02 submission/methods.tex
minor edits

Let us write the objective/optimization function (parameterized by $\mathbf{W}_{l}$s and $\mathbf{b}_{l}$s) for a DNN with $L$ layers, activation functions $h_{l}(\cdot)$, and $N\times M$ weight matrices $\mathbf{W}_{l}$ and biases $\mathbf{b}_{l}$,~as:
\begin{equation}
E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})  .
\label{eqn:dnn_energy}
\end{equation}
Each DNN layer contains one or more layer 2D  $N\times M$ weight matrices, $\mathbf{W}_{l}$, or pre-activation maps, $\mathbf{W}_{i,l}$, extracted from 2D Convolutional layers, and where $N > M$.% 
\footnote{We do not use intra-layer information from the models in our quality metrics, but (as we will describe) our metrics can be used to learn about intra-layer model properties.}
(We may drop the $i$ and/or $i,l$ subscripts below.)
See Appendix~\ref{sxn:appendix} for how we define the Conv2D layer matrixes and for our choices of normalization.

>>>>

Let us write the objective/optimization function (parameterized by $\mathbf{W}_{l}$s and $\mathbf{b}_{l}$s) for aE DNN with $L$ layers, activation functions $h_{l}(\cdot)$, and $N\times M$ weight matrices $\mathbf{W}_{l}$ and biases $\mathbf{b}_{l}$,~as \nred{the minimization of a general Loss Function $\mathcal{L}$ over  N (labeled) training data instances $(\mathbf{x}_{i},y_{i})$. For a typical supervised classification problem, one has
\begin{equation}
\underset{\mathbf{W}_{l},\mathbf{b}_{L}}{\text{argmin}}\;\sum_{i=1}^{N}\left(\mathcal{L}(E_{DNN}(\mathbf{x}_{i})-y_{i})\right)
\end{equation}
where }
\begin{equation}
E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L}),
\label{eqn:dnn_energy}
\end{equation}
\nred{the loss function $\mathcal{L}()$ can take on a myriad of forms\cite{Janocha2017}, and $E_{DNN}$ is what we call the Energy Landscape.}

Each DNN layer contains one or more layer 2D  $N\times M$ weight matrices, $\mathbf{W}_{l}$, or pre-activation maps, $\mathbf{W}_{i,l}$, extracted from 2D Convolutional layers, and where $N > M$.% 
\footnote{We do not use intra-layer information from the models in our quality metrics, but (as we will describe) our metrics can be used to learn about intra-layer model properties.}
(We may drop the $i$ and/or $i,l$ subscripts below.)
See Appendix~\ref{sxn:appendix} for how we define the Conv2D layer matrixes and for our choices of normalization.
